\documentclass{article}
\author{Nick Kunz}

% dependencies
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{fontawesome5}
\usepackage[none]{hyphenat}
\usepackage[most]{tcolorbox}

\geometry{margin = 0pt}

\definecolor{seagreen}{HTML}{A1BF49}
\definecolor{wowgreen}{HTML}{E5FF63}

\hypersetup{
    colorlinks = true,
    urlcolor = seagreen,
    allbordercolors = wowgreen
}

\newtcolorbox{bgbox}[1][]
    {nobeforeafter,leftright skip=0pt,boxrule=0pt,enhanced jigsaw,sharp corners,#1}

\renewcommand{\baselinestretch}{1.025}

\begin{document}
\noindent
\scriptsize
\fontdimen2\font = 1pt
    \begin{bgbox}[
        height = \paperheight,
        width = 0.3\textwidth,
        colback = gray
    ]
        \textcolor{white}{
            \section*{Nick Kunz}
            \section*{\textit{\normalsize{Senior Data Scientist}}}
                Address: \space\space\space 602 Rhodes Hall, Ithaca, NY\newline
                Mobile: \space\space\space\space +1 $($602$)$ 710-8608\newline
                Email: \space\space\space\space\space\space\space\url{nick.kunz@me.com}\newline
                Website: \space\space\space\url{nickkunz.com}
            \section*{Skills}
                Generative AI, Large Language Models (LLMs)\newline
                Machine Learning, Simulation, Optimization\newline
                System Design, Cloud Architecture\newline
                Containers, Deployment, Testing\newline
                Geographic Information Systems (GIS)\newline
                Financial Modeling, Forecasting
            \section*{Languages}
                \textbf{Scripting}: Python, Bash\newline
                \textbf{Statistical}: R, Stata\newline
                \textbf{Compiled}: C/C++, Fortran\newline
                \textbf{Database}: SQL, NoSQL, Cypher\newline
                \textbf{Typesetting}: \LaTeX, Markdown
            \section*{Frameworks}
                \textbf{Data Science}: NumPy, SciPy, Pandas\newline
                \textbf{Statistical Learning}: SKLearn, XGBoost\newline
                \textbf{Prompt Engineering}: LangChain, Bedrock\newline
                \textbf{Data Visualization}: React, Streamlit\newline
                \textbf{Deep Learning}: Pytorch, TensorFlow
            \section*{Deployment}
                \textbf{DevOps}: Git, Docker, CI/CD \newline
                \textbf{Databases}: PostgreSQL, SQLite, Neo4j\newline
                \textbf{Web Services}: Flask, Gunicorn, Nginx\newline
                \textbf{Web Automation}: Selenium, Puppeteer\newline
                \textbf{Cloud Platforms}: Azure, AWS, GCP\newline
                \textbf{Security}: OWASP ZAP, STIGs
            \section*{Environments}
                \textbf{Development}: VS Code, Databricks, RStudio\newline
                \textbf{Geospatial}: ArcGIS, QGIS, OSM, Leaflet\newline
                \textbf{3D Modeling}: Rhino, Grasshopper\newline
                \textbf{Design \& Illustration}: Adobe Suite\newline
                \textbf{Financial Modeling}: Excel, Macros\newline
                \textbf{Studio \& Live Audio}: Logic, Protools
            \section*{Prototyping}
                \textbf{Project Management}: Agile, Scrum\newline
                \textbf{Sensors \& Hardware}: Arduino, Rasp. Pi,\newline
                \textbf{Electrical}: Soldering, Wiring, Safety\newline
                \textbf{Ideation}: Drawing, Sketching, Storyboarding\newline
                \textbf{Analogs}: Hand Drafting, Physical Modeling
            \section*{Awards}
                Graduate Engineering Fellowship, 2024\newline
                Systems Engineering Fellowship, 2023\newline
                AVID Applause Award, 2022\newline
                Distinguished Alumni Award, 2016\newline
                AmeriCorps Education Award, 2014\newline
                Dingwall Foundation Scholarship, 2012\newline
                Appraisal Institute Scholarship, 2011
        }
    \end{bgbox}
    \begin{bgbox}[
        height = \paperheight,
        width = 0.69\textwidth,
        colback = white
    ]
    \linespread{0.95}
        \textcolor{black}{
            \section*{Experience}
                \textbf{Deloitte} | Seattle, WA\hfill{2021 - 2024}\newline
                    Senior Data Scientist\newline\newline
                Technical lead on the development and deployment of machine learning services for grant funding of clinical research and public health. Detailed analyses of PubMed Knowledge Graph utilized for marketing managed services in support of awarded contract with NIAID. Development of Retrieval-Augmented Generation LLM applications for AI quality.\newline\newline
                \textbf{Microsoft} | Redmond, WA\hfill{2020 - 2021}\newline
                    Data Scientist\newline\newline
                Developed performance metrics, methodologies, synthetic data, and models into production ready prototypes for the Integrated Visual Augmentation System $($IVAS$)$ to improve performance and safety of Infantry units in the US Army through Microsoft’s HoloLens technology and its mixed reality training environment. \textit{Contract: Aquent.}\newline\newline
                \textbf{Pacific Prospecting Group} | Seattle, WA\hfill{2017 - 2019}\newline
                    Data Scientist\newline\newline
                Developed proprietary prediction systems to automate ‘hopping’ between hashing algorithms for maximizing cryptocurrency mining revenue. Assisted with infrastructure development in collaboration with electrical engineers on bitstream development.\newline\newline
                \textbf{Brawner \& Company} | Snoqualmie, WA\hfill{2016 - 2017}\newline
                    Development Analyst\newline\newline
                Provided consulting services and financial modeling for tax-credit equity generating real estate investments. Lead detailed analyses utilizing statistical modeling. Automated a reconciliation system for operating cost budgets totaling over \$2.7M annually. Financial forecasts used in capital improvements totaling over \$30M.
                \newline\newline
                \textbf{bcWORKSHOP} | Dallas, TX\hfill{2013 - 2014}\newline
                    Fellow\newline\newline
                Conducted a novel county-wide geospatial analysis of children's asthma rates utilizing advanced GIS to identify 2 strategic subject sites for an indoor air quality pilot program. Served as a committee member in a multidisciplinary collaborative to improve the lives of over 60,000 children that suffer from debilitating asthma in Dallas County.
            \section*{Education}
                \textbf{Cornell University} | Ithaca, NY\hfill{2026}\newline
                        PhD, Systems Engineering, Artificial Intelligence\newline
                            \textit{Thesis: Global Geolocated Realtime Data of Interfleet Urban Transit Bus Idling}\newline\newline
                \textbf{Columbia University} | New York, NY\hfill{2019}\newline
                        MS, Urban Planning, Urban Analytics\newline
                            \textit{Thesis: Unsupervised Learning for Submarket Modeling: A Proxy for Neighborhood Change}\newline\newline
                % \textbf{Harvard University} | Cambridge, MA\hfill{2012}\newline
                %         Urban Planning\newline
                %             \textit{Capstone: Fenway-Kenmore Comprehensive Planning \& Finance}\newline\newline
                \textbf{Arizona State University} | Tempe, AZ\hfill{2012}\newline 
                        BS $($Hons$)$, Housing \& Urban Development\newline
                            \textit{Thesis: Realizing Interactive Architecture: A Driver of the Knowledge Economy}
            \section*{Software}
            \textbf{SMOGN: Synthetic Minority Over-Sampling Technique for Regression with Gaussian Noise}\hfill{2021}\newline
            \faGithub\space Github [ \href{https://github.com/nickkunz/smogn}{\texttt{Link}} ] \space\faPython\space PyPI\space [ \href{https://pypi.org/project/smogn}{\texttt{Link}} ]\space\faUsers\space Kaggle [ \href{https://www.kaggle.com/aleksandradeis/regression-addressing-extreme-rare-cases}{\texttt{Link}} ]\newline\newline
            A novel pre-processing algorithm designed to address imbalanced data for regression problems. Conducts over-sampling with traditional interpolation, as well as with the introduction of Gaussian noise. Selects between the two over-sampling techniques by the KNN distances underlying a given observation.\newline\newline
            \textbf{NestedHyperBoost: Nested Cross-Validation for Bayesian Optimized Gradient Boosting}\hfill{2020}\newline
            \faGithub\space Github [ \href{https://github.com/nickkunz/nestedhyperboost}{\texttt{Link}} ] \space\faPython\space PyPI\space [ \href{https://pypi.org/project/nestedhyperboost}{\texttt{Link}} ]\newline\newline
            Unifies Nested K-Fold Cross-Validation, Bayesian Hyperparameter Optimization, and Gradient Boosting. Designed for rapid prototyping on small to mid-sized data sets. Quickly obtains high quality prediction results by abstracting away tedious hyperparameter tuning and implementation details in favor of usability and implementation speed.
            \section*{Military}
                \textbf{US Army, 75th Ranger Regiment} | Fort Lewis, WA \hfill{2015 - 2016}\newline
                        Infantry\newline\newline
                            Served in support of US Army Special Operations as a US Army Ranger at 2nd Ranger Battalion. Developed deep interpersonal skills in leadership, problem-solving, perseverance, and teamwork. Mission focus dedicated to airfield seizures, direct action raids and ambushes. \textit{Discharge: Honorable.}\newline\newline
                \textbf{US Army, 1st Special Warfare Training Group} | Fort Bragg, NC \hfill{2014}\newline
                        Special Forces Candidate\newline\newline
                            Training and indoctrination assignments include: US Army Ranger Assessment and Selection Program, US Special Forces Assessment and Selection, US Special Forces Preparation and Conditioning, US Army Airborne School, and US Army Infantry School.\newline
            \mbox{}
            \vfill
            % \hfill{}\textit{Updated: March 2024}
        }
    \end{bgbox}
\end{document}